Example and Tutorial for Vim Editor (Linux)

### 2020-01-05 nontex/install/linux/fn_vim.Rmd
r project template folder to reuse

1. Delete:
    - delete current word and go into insert mode: *ciw*
    - Delete current word: *dw*
    - Delete from cursor until end of sentence: *dis*
    - Delete from cursor to end of line: *d$* or *D*
    - Delete until end of paragraph: *dip*
    - Delete all text in file: *ggdG*

>>>>

1. Delete
    - delete current word and go into insert mode: *ciw*
    - Delete current word: *dw*
    - Delete from cursor until end of sentence: *dis*
    - Delete from cursor to end of line: *d$* or *D*
    - Delete until end of paragraph: *dip*
    - Delete all text in file: *ggdG*
2. Copying: replace *d* by *y* for all oeprations.
    - Copy current word: *dw*
    - Copy from cursor to end of line (need to set this): *y$* or *Y*
    - Copy until end of paragraph: *yip*
3. Insert to edit:
    - Insert after last character of document: *GA*
    - Insert at the end of line: *A*
    - Insert after cursor, *a*, insert before curosr *i*
